---
title: "Datalicious Depths of Delectable Data"
output: 
  html_document: 
    fig_caption: TRUE
date: "2023-08-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
library(dplyr)
library(plotly)
library(ggplot2)
library(distill)
library(rmarkdown)
library(RColorBrewer)
library(formattable)
library(kableExtra)
library(patchwork)
library(gridExtra)
library(cowplot)
library(countrycode)
library(maps)


# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```


Want to jump to a specific question? 

- [Which results are the most common?](#popres)
- [How do results vary between countries?](#country) 
- [Are all questions created equal?](#questions)

### Which results are the most common? <a name="popres"></a>

See, if Open Psychometrics recorded the respondents' results, it would be quite quick to answer this question. Unfortunately, they didn't, and we're working with a bunch of numbers! 

This is what the data looks like: 


```{r, initialdata, include=FALSE}
data <- read.csv("country.csv")
#data <- sapply(data[,!(names(data) %in% c("country"))], as.numeric)
#data["country"] <- as.character(data["country"])
options(scipen=10000) 
```

```{r, begin data}
paged_table(head(data))
```

I've selected the first 6 columns.. and it's not too bad! It's a little intimidating to think that there are over 1 million more rows, but we've gotta start somewhere >:)

We start by calculating the scores for the 'Extroversion' personality trait. We can do this by summing up the scores of the 10 EXT (standing for EXTroversion) questions. However, it should be noted that answering a '4' or '5' on a EXT question doesn't always mean that a user is more extroverted. For example, answering 5 for "I don't talk a lot" vs "I am the life of the party" would significantly affect your results. 

So, we'll need to make sure to add and subtract scores as necessary, depending on how the questions are keyed. I've arbitrarily made the decision to 
'positively key' questions symbolising extroversion (meaning that I'd add points to their total score if they showed signs of extroversion), and 'negatively key' questions symbolising introversion (subtracting points from total score). See the table below to better understand this keying: 


```{r, exttablekey}

keyta = data.frame('Questions' = c("I am the life of the party.", "I don't talk a lot.", "I feel comfortable around people.", "I keep in the background.", "I start conversations.", "I have little to say.", "I talk to a lot of different people at parties.", "I don't like to draw attention to myself.", "I don't mind being the center of attention.", "I am quiet around strangers."), 
                    'Key' = c('$+$', "$-$", '$+$', "$-$",'$+$', "$-$",'$+$', "$-$",'$+$', "$-$"))

kable(keyta, caption = "EXT Question Key") %>%
  kable_styling()

## plus signs don't appear? 

```


Hence, after adding/subtracting their points from each question, any positive total score (> 0) will mean that the user receives an 'S' for Sociable, while a negative score (< 0) would result in an 'R'.^[Recall how introverted questions are negatively keyed and subtracted from your total.] If their score is 0, then they'd receive an 'X', as their results since they're perfectly in-between, and will remain inconclusive.

Below is a sample table of results, where extletter (their final letter result) and extscore (the sum of their points) are calculated from the raw data. 

```{r, extdata}


exttable <- data %>% 
  select(starts_with('EXT'))  

exttable <- exttable %>% select(-c (ends_with('E'))) %>% 
  mutate(extscore = EXT1 - EXT2 + EXT3 - EXT4 + EXT5 - EXT6 + EXT7 - EXT8 + EXT9 - EXT10) %>% 
  mutate(extletter = 
    case_when(
      extscore > 0 ~ "S", 
      extscore < 0 ~ "R", 
      extscore == 0 ~ "X"
    )) %>%
  select(extletter, extscore, everything())
paged_table(head(exttable))

```

<br>
We can also visualize our results into a graph: 

```{r, extgraph}
exttable <- data %>% select(starts_with('EXT'))
exttable <- exttable %>% select(-c (ends_with('E'))) %>% 
  mutate(extscore = (EXT1-3) - (EXT2-3) + (EXT3-3) - (EXT4-3) + (EXT5-3) - (EXT6-3) + (EXT7-3) - (EXT8-3) + (EXT9-3) - (EXT10-3)) %>% 
  mutate(extletter = 
    case_when(
      extscore > 0 ~ "S", 
      extscore < 0 ~ "R", 
      extscore == 0 ~ "X"
    ))

dfext <- data.frame(extlettercount = c(500346, 468068, 45144),
                    extlettermap = c('R', 'S', 'X'))


 pext <- ggplot(data=dfext, aes(x=extlettermap, y=extlettercount)) +
   geom_bar(stat="identity", fill="steel blue") +
   labs(
     title = "Responders are More Introverted Than Extroverted",
     subtitle = "Introverts, give me a cheer! Wait... why is it silent? Where did the introverts go?") + 
   xlab("Possible Results") +
   ylab("Amount of Responses")+
   geom_text(aes(label=extlettercount), vjust=-0.3, size=3.5)+
   theme_minimal()
 pext

```

The same processes will be applied to the other personality traits, with their graphs located below: 


```{r, est}
 esttable <- data %>% select(starts_with('EST'))
 esttable <- esttable %>% select(-c (ends_with('E'))) %>%
   mutate(estscore = (EST2-3) - (EST1-3) - (EST3-3) + (EST4-3)  - (EST5-3)- (EST6-3)- (EST7-3)- (EST8-3)- (EST9-3)- (EST10-3)) %>%
   mutate(estletter =
            case_when(
              estscore > 0 ~ "C",
              estscore < 0 ~ "L",
              estscore == 0 ~ "X"
            ))
 
 dfest <- data.frame(estlettercount = c(517196, 452040, 44322),
                     estlettermap = c('L', 'C', 'X'))

 plotest <- ggplot(data=dfest, aes(x=estlettermap, y=estlettercount)) +
   geom_bar(stat="identity", fill="steel blue") +
   labs(
     title = "Respondents are More Prone
to Being Limbic Than Calm",
     subtitle = "Moody and a little bit groovy") + 
   xlab("Possible Results") +
   ylab("Amount of Responses")+
   geom_text(aes(label=estlettercount), vjust=-0.3, size=3.5)+
   theme_minimal()+
   scale_y_continuous(expand = c(0.1, 0))

```

```{r, csn}
 csntable <- data %>% 
  select(starts_with('CSN'))


 csntable <- csntable %>% select(-c (ends_with('E'))) %>% 
   mutate(csnscore = (CSN1-3) - (CSN2-3) + (CSN3-3) - (CSN4-3) + (CSN5-3) - (CSN6-3) + (CSN7-3) - (CSN8-3) + (CSN9-3) + (CSN10-3)) %>% 
   mutate(csnletter = 
            case_when(
              csnscore > 0 ~ "O", 
              csnscore < 0 ~ "U", 
              csnscore == 0 ~ "X"
            ))
 
 dfcsn <- data.frame(csnlettercount = c(662846, 302063, 48649),
                     csnlettermap = c('O', 'U', 'X'))
 
 pcsn <- ggplot(data=dfcsn, aes(x=csnlettermap, y=csnlettercount)) +
   geom_bar(stat="identity", fill="steel blue") +
   labs(
     title = "Responders Tend to be
Organized, Rather Than\nUnorganized",
     subtitle = "Control freaks reign supreme") + 
   xlab("Possible Letters") +
   ylab("Amount of Responses")+
   geom_text(aes(label=csnlettercount), vjust=-0.3, size=3.5) +
   theme_minimal()+
   scale_y_continuous(expand = c(0.1, 0)) 
 
 plot_grid(plotest, pcsn, ncol = 2, align = "hv")
 
```

```{r, agr}
 agrtable <- data %>% select(starts_with('AGR'))
 agrtable <- agrtable %>% select(-c (ends_with('E'))) %>% 
   mutate(agrscore = (AGR2-3) - (AGR1-3) + (AGR4-3) - (AGR3-3) + (AGR6-3) - (AGR5-3) + (AGR8-3) - (AGR7-3) + (AGR10-3) + (AGR9-3)) %>% 
   mutate(agrletter = 
            case_when(
              agrscore > 0 ~ "A", 
              agrscore < 0 ~ "E", 
              agrscore == 0 ~ "X"
            ))

dfagr <- data.frame(agrlettercount = c(846333, 140674, 26551),
                     agrlettermap = c('A', 'E', 'X'))
 
 plotagr <- ggplot(data=dfagr, aes(x=agrlettermap, y=agrlettercount)) +
   geom_bar(stat="identity", fill="steel blue") +
   labs(
     title = "Respondents Rate Themseleves
More Agreeable Than Egocentric",
     subtitle = "AKA: People like to think they're a lot nicer
than they actually are") + 
   xlab("Possible Letters") +
   ylab("Amount of Responses")+
   geom_text(aes(label=agrlettercount), vjust=-0.3, size=3.5) +
   theme_minimal()+
   scale_y_continuous(expand = c(0.1, 0))
 
```

```{r, opn}
 opntable <- data %>% select(starts_with('OPN'))
 opntable <- opntable %>% select(-c (ends_with('E'))) %>% 
   mutate(opnscore = (OPN1-3) - (OPN2-3) + (OPN3-3) - (OPN4-3) + (OPN5-3) - (OPN6-3) + (OPN7-3) + (OPN8-3) + (OPN9-3) + (OPN10-3)) %>% 
   mutate(opnletter = 
            case_when(
              opnscore > 0 ~ "I", 
              opnscore < 0 ~ "N", 
              opnscore == 0 ~ "X"
            )) 
 
dfopn <- data.frame(opnlettercount = c(902605, 85372, 25581),
                     opnlettermap = c('I', 'N', 'X'))
 
 plotopn <- ggplot(data=dfopn, aes(x=opnlettermap, y=opnlettercount)) +
   geom_bar(stat="identity", fill="steel blue") +
   labs(
     title = "The Majourity Considers 
Themselves as Inquisitive",
     subtitle = "BREAKING: People like learning,\nschools are just ineffective...\nallegedly") + 
   xlab("Possible Letters") +
   ylab("Amount of Responses")+
   geom_text(aes(label=opnlettercount), vjust=-0.3, size=3.5) +
   theme_minimal() +
   theme(plot.margin = unit(c(0.5,0.5,0.5,1),"cm")) +
   scale_y_continuous(expand = c(0.1, 0))

#scale_x_continuous(limits = c(min(opnlettercount),max(opnlettercount)+5))


 
  plot_grid(plotagr, plotopn, ncol = 2, align = "hv")

 
```

Now, we can combine everybody's letters from each personality traits to form their final result, then determine which results are the most common within this data set. 

In fact, we can see the 25 most common results below: 

```{r, combineresults}
finalletters <- c(paste(exttable$extletter, esttable$estletter, csntable$csnletter, agrtable$agrletter, opntable$opnletter, sep=""))
 finaltable <- data.frame(finalletters) 
  
 pfinaltable25 <- finaltable %>% 
   unnest(finalletters) %>%
   group_by(finalletters) %>%
   summarize(total = n()) %>%
   arrange(desc(total)) %>%
   slice(1:25)
 getPalette = colorRampPalette(brewer.pal(9, "Set1"))
 
  blank_theme <- theme_minimal()+
   theme(
     axis.title.x = element_blank(),
     axis.title.y = element_blank(),
   )
 
 bp25 <- ggplot(pfinaltable25, aes(x="", y=total, fill=reorder(finalletters, -total))) +
   geom_bar(width = 1, stat = "identity") +scale_fill_manual(values = getPalette(25))
 
 pie25 <- bp25 + coord_polar("y", start=0) 
 pie25 + blank_theme + theme(axis.text.x=element_blank()) +
   labs(title="Top 25 Most Common Results", 
        fill="Results")
 
```

<br>
WOOO! Congratulations to the XXOAI family for being among the most common result out of 243 possibilities! 

If you'd prefer to see a more numerical representation, I've provided a table with the exact number of each result and the average score of each personality trait^[The average values will actually shift every time I update the website (on RStudio!), as the function 'slice_sample' will grab the average of 100 randomly selected responses, resulting in a unique average every time!]: 
<br>

```{r}

 pfinaltable <- finaltable %>% 
    unnest(finalletters) %>%
   group_by(finalletters) %>%
    summarize(total = n()) %>%
   arrange(desc(total)) %>%
   slice(1:10)
 
 pfinaltable <- pfinaltable %>% 
   mutate(percentage = total/1015342 * 100)

   
colnames(pfinaltable) <- c("Results", "Amount of Responses", "Percentage of People")
knitr::kable(pfinaltable,
             caption = "The 10 Most Common Results") %>% 
  kable_styling()
 
```

```{r, avgtrait}
#checking average score of each section 

avgscore <- cbind(exttable$extscore, esttable$estscore, csntable$csnscore, agrtable$agrscore, opntable$opnscore)
avgscore <- data.table::as.data.table(avgscore, .keep.rownames = "word")
  
avgscore <- slice_sample(avgscore, n=75) %>%
  colMeans() 

avgscore <- data.table::as.data.table(avgscore, .keep.rownames = "word")
avgscore <- as.data.frame(t(avgscore))

colnames(avgscore) <- c("Extroversion", "Neuroticism", "Conscientiousness", "Agreeableness", "Openness")

kable(avgscore, caption = "Average Score for Each Personliaty Trait") %>% 
  kable_styling()

```


### Let’s try to analyze why these results happened.

**Extrovertism**

Extrovertism is the most balanced trait, as there seems to be a nice mix of S(ocial) and R(eserved) – representative of the larger population. I’d assume this is because questions in this trait were very straight-forward (e.g. “I start conversations”), and users likely display/are conscious of these behaviors in their everyday life. Hence, with a more ‘objective’ viewpoint, this removes the issue of self-bias and leads to more accurate results. 

There are also about ~40k more introverts compared to extroverts. Maybe the S’s aren’t as likely to spend 20 minutes on an online test, compared to R’s? 


**Neuroticism**

Once again, a solid distribution of results between C(alm) and L(imbic), mirroring what I’d expect the general population to be like. Similar to the extrovertism section, the questions tend to be straightforward and there’s relatively less self-bias within the trait, as many people are conscious of their emotions, and whether or not they control them.  

There are ~60000 more limbic people compared to calm. I’m not really surprised - people are more stressed^[https://www.wbur.org/hereandnow/2022/07/13/stress-survey-gallup] and more sad^[https://www.voanews.com/a/why-people-worldwide-are-unhappier-more-stressed-than-ever-/6658784.html] than we’ve ever been. Furthermore, emotional regulation is a result of introspection and reflection. As our society slowly moves towards constant stimulation and excess, it’s no wonder we struggle to achieve emotional stability. 

**Conscientiousness, Agreeableness, and Openness**

With these three traits, we start to see a much larger gap between the possible letters. There are significantly more people that are organized, agreeable, and inquisitive, relative to unstructured, egocentric, and non-inquisitive. 

I definitely don’t think these results reflect the general population, despite the fact that I have no evidence stating so. If I had to speculate, I’d say that this data is just a *tiny* bit biased, leading to skewed results. 

1. We’re just a little bit tainted 

No matter how hard we try, we can never be completely objective. Many struggle to see things beyond ourselves, to judge every action we take from a neutral standpoint. 

In normal, everyday life, this is not too significant of an issue. A little bit of subjectivity never hurt anybody! However, when we’re trying to objectively analyze and record data about ourselves, since this is a self-administered quiz, our lack of objectivity can lead to delusional answers.

2. We’re fragile creatures

For these three categories, there are clear ‘winners’. In this society, it is almost ALWAYS better if you’re organized, agreeable, and inquisitive, rather than the opposite. In fact, it’s almost an insult if we AREN’T these things, because that means we should ‘be better’.^[If someone told you, “Yea, you’re just a bit egocentric… no offense”, would you be happy about it?] For example, you may want to be agreeable and people-pleasing, since it shows that you’re friendly and nice, and people will tend to ‘like’ you more, instead of if you’re confrontational and assertive for your own needs. Or, as our society moves towards maximizing productivity and ‘grind culture’, you NEED to be conscientious and self-disciplined, or else you won’t be successful.  Or, people don’t want to be seen as rigid and unwilling to try new things. Society will call them scaredy-cats, boring, or that you’re ‘bringing the mood down’. 

It doesn’t help that we don’t like being ‘bad people’ – we constantly attempt to justify our actions to be good and perceive ourselves in a positive light. We are rarely the villains in our own stories; it’s always the other person doing something wrong, or doing something worse than we did, or they started the ordeal.

However, when we can’t be objective, we can confuse what we actually do, to what we wish we did. This is going to lead us to choose answers corresponding to those ‘better’ traits of self-discipline, agreeableness and inquisitiveness, instead of objectively saying we have the ‘worse’ traits of unstructuredness, egocentrism and un-inquisitiveness.

3. We’re just built for this (for Openness)

There’s also the classic case of sampling bias. The people who take this quiz are probably curious about psychology, want to know more about themselves, and are willing to try something new. These are typically the types of people who are inquisitive (matching with the I letter) instead of non-inquisitive (matching with the N letter). 


**Sheer Statistical Impossibility...?** 

However, When analyzing this data, it seems.. strange that so many __OAI types are represented. In fact, it feels weird that 15%(!!!!) of people were the EXACT SAME TYPE, despite ALL POSSIBLE COMBINATIONS! 

So, let's see how it compares to the theoretical data. Using the data^[This was the only site that had theoretical values. I don't know where they got their percentages from, and there was also no data on certain combinations. It should also be noted that this site does not use 'X' as a possible result. E.g. XLUEI (or any combination with an 'X') is not considered. So this source can not be completely trusted. It should also be noted that SimilarMinds separates the theoretical values by female and male. Since this data set does not have this distinction, I used the average of the male and female theoretical values to get my average number.] from [SimilarMinds](https://similarminds.com/global5/rcoai.html), we can see how our data stacks up. 


```{r}

 theorytable <- select(pfinaltable, Results) %>%
   mutate("Percentage of People" = c(3.4, 2.7, 2.5, 3.5, "N/A", 3.4, 4.1, "N/A", "N/A", "N/A"))

expertable <- select(pfinaltable, "Results", "Percentage of People")


knitr::kables(list(
  kable(caption = "Theoretical Data",
    theorytable) %>% kable_styling(),
    kable(caption = "Experimental Data",
     expertable
    ) %>% kable_styling()
    
  )
) %>% kable_styling()

```


Looking at these tables, there’s a clear discrepancy between theoretical and experimental data, where none of the theoretical results really match up to what is seen in our data set -- certain results are far more represented than the average value. 

However, most of it can be explained by the previous analysis: Wrong results might occur because of biases and societal norms (cementing the last two letters to be A and I), in addition to the natural disposition of respondents. 

Honestly, I’m not too sure why 15% of people are SCOAI, maybe people are being influenced to answer what they WANT to be like, rather than what they actually are, since SCOAI seems like one of the most 'socially-successful’ results.^[Extroverted, stable, organized, agreeable, and inquisitive are all attributes that allow people to thrive, as they will tend to have larger social circles, better intrapersonal relationships and private lives, and the ability to study and work hard to get to positions they want academically and corporately.] So, in reality, I think that many respondents are not actually SCOAIs. That’s my best guess!^[If you have more ideas, I’d love to hear them! Reach out :)]

Also, just to provide a comphrensive review of the results, here's a list of the most uncommon ones! 

```{r, unpoptable}
pfinaltableasc <- finaltable %>% 
  unnest(finalletters) %>%
  group_by(finalletters) %>%
  summarize(total = n()) %>%
  arrange(total) %>%
  slice(1:10)

colnames(pfinaltableasc) <- c("Results", "Amount of Responses")

knitr::kable(pfinaltableasc,
             caption = "Most Uncommon Results") %>% kable_styling(position = "center")

```

No surprise, it's a lot of results with X's!

At first, I was surprised that 'XXXXX' didn't appear, since I'd assume it (theoretically) is the most unlikely.^[There's actually 3794 people who got  XXXXX in this data set] However, I wouldn't be surprised if only 5% of respondents were genuinely XXXXX, while the other 95% of people who got the result just kept clicking 3 (Neutral) for every question, or had some kind of game to see if they could get the (theoretically) super rare XXXXX. 

### Do results vary between countries? <a name="country"></a>

This data contains 224 unique ISO country codes^['Country codes' are kinda misleading. There are ~195 countries, and ISO has 249 different codes. This is because the ISO contains subdivisions of countries, e.g. Caymen Islands (UK) and Christmas Island (Australia)]. Let's dig through this data - a fun bit of stalking!

```{r, country data}


countres <- data %>% 
  select('country') %>%
  group_by(country) %>%
  summarize(total = n()) %>%
  arrange(desc(total)) %>% 
  slice(1:25)


ggplot(data= countres, mapping = aes(x = reorder(country, -total), y = total))+
  geom_col(fill = "steelblue")+
  theme_classic()+
  labs(title = "Locations of Respondents", 
       subtitle = "OH SAY, CAN YOU SEEEEE!", 
       y = "Amount of Responses", 
       x = "Location")

```

We can see that the majority of data came from the US, with a whopping total of 546403 respondents. Trailing (very far) behind, we also have Great Britain (GB), Canada (CA), and Australia (AU). 

This is likely because this quiz is in English, and will generally cater towards countries with English as their primary language. In addition, Google's SEO (Search Engine Optimization) is also affected by location, and can rank websites by their proximity to the user.^[https://www.searchenginejournal.com/ranking-factors/physical-proximity-to-searcher] So, it's possible that Open Psychometrics is American^[I couldn't find any location data on the website itself], and when Americans search up "Big Five Personality Test", this would be the first quiz that shows up.^[As a Canadian, it's actually the third search result!]

But, we're not really concerned on WHERE people are taking the quiz. Instead, we only care about how it affects the responses. Hence, we're going to start by finding the most common results for America, Great Britain, Australia, and the Philippians --these location shave the most amount of results while being from different continents-- and seeing how they compare to one another. 

```{r}
coutdata <- cbind(finaltable$finalletters, data$country) 


## US Data 
colnames(coutdata) <- c('Results', 'Country')
coutdata <- data.table::as.data.table(coutdata, .keep.rownames = "word")

usdata <- coutdata[coutdata$Country %in% "US"]

usdataslice <- usdata %>% 
  select('Results') %>%
  group_by(Results) %>%
  summarize(Percentage = n()/546403*100) %>%
  arrange(desc(Percentage)) %>% 
  slice(1:10)


## GB
gbdata <- coutdata[coutdata$Country %in% "GB"]
colnames(gbdata) <- c('Results', 'Country')

gbdataslice <- gbdata %>% 
  select('Results') %>%
  group_by(Results) %>%
  summarize(Percentage = n()/66596*100) %>%
  arrange(desc(Percentage)) %>% 
  slice(1:10)



#Aus
audata <- coutdata[coutdata$Country %in% "AU"]
colnames(audata) <- c('Results', 'Country')

audataslice <- audata %>% 
  select('Results') %>%
  group_by(Results) %>%
  summarize(Percentage = n()/50030*100) %>%
  arrange(desc(Percentage)) %>% 
  slice(1:10)

##Ph
phdata <- coutdata[coutdata$Country %in% "PH"]
colnames(phdata) <- c('Results', 'Country')

phdataslice <- phdata %>% 
  select('Results') %>%
  group_by(Results) %>%
  summarize(Percentage = n()/19847*100) %>%
  arrange(desc(Percentage)) %>% 
  slice(1:10)


knitr::kables(list(
  kable(caption = "America", usdataslice) %>% kable_styling(),
  kable(caption = "Great Britian", gbdataslice) %>% kable_styling(),
  kable(caption = "Australia", audataslice) %>% kable_styling(),
  kable(caption = "Philippines", phdataslice) %>% kable_styling()
  )
) %>% kable_styling()

```


From the above table, it's pretty clear that countries have very similar trends, with the top 7 result virtually the same between all countries. However, there are slight differences you can take out of it: 

- The Philippines tends to be more introverted than extroverted 
- The Philippines tends to be more limbic than calm 
- The Philippines is the only location to have an 'X' appear in their results
- The Philippines contains the only 'N', instead of 'I'
- Great Britain has the 'least variation' in regard to percentage (Their percentage column has the smallest range)
- 'E' only appears 7 times, relative to the 33 appearances of 'A'
- Every result in this table also appears in the top 25 most common results


Let's try zooming out by plotting the averages on a world map, and then analyzing results. 

A note on the data: Locations with less than 10 responses have been omitted from the data, as they often significantly skewed maps. This removed 58 locations off the map, with Africa losing a pretty big chunk of their land. 


```{r extscores world map, layout="l-body-outset", fig.cap="Diamond sadasds"}

exttablec <- exttable %>% 
  cbind(data$country)

colnames(exttablec)[13] <- "region"

redcount <- c('AS', 'RE', 'CK', 'NC', 'PF', 'TC', 'TL', 'VU', 'XK', 'LI', 'MP', 'SL', 'FM', 'LR', 'MC', 'MQ', 'SS', 'SH', 'TO', 'AI', 'GA', 'GP', 'SX', 'CD', 'CG', 'ML', 'MR', 'PW', 'TG', 'VG', 'AQ', 'BF', 'BJ', 'BQ', 'DJ', 'GF', 'MS', 'NU', 'PM', 'SM', 'TJ', 'BI', 'FK', 'GN', 'GQ', 'KM', 'MF', 'MH', 'NE', 'SH', 'TD', 'NE', 'TD', 'PW', 'KM', 'TJ', 'GQ', 'ML')


exttablec <- exttablec %>%
  group_by(region) %>%
  drop_na 

for (i in redcount) {
  exttablec<- subset(exttablec, region!=i)
}


extworld <- exttablec %>% 
  group_by(region) %>%
  summarize(ExtScores = mean(extscore))



world_map = map_data("world") 
world_map$region <- countrycode(world_map$region, "country.name", "iso2c")  

colnames(world_map)[1] <- "Longitude"
colnames(world_map)[2] <- "Latitude"


mergemapext <- inner_join(world_map, extworld, by = "region")


pext <- ggplot() +
  geom_polygon(data=mergemapext,
          aes(x=Longitude, y=Latitude, group=group, fill = ExtScores, label=region),
          color="white", size = 0.2) + 
  coord_cartesian(ylim = c(-50, 90)) + 
  labs(
    title="Extroversion Scores of the World",
    fill="Extroversion
Averages", 
  )+ theme_minimal() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.x = element_blank(),axis.title.y = element_blank())

ggplotly(pext)


```

Higher scores are correlated with extroversion, lower scores are correlated introversion. 

```{r, extworldtable}

topext <- extworld %>%
  arrange(ExtScores) %>%
  head()

topext$region<- countrycode(topext$region, "iso2c", "country.name")

botext <- extworld %>%
  arrange(desc(ExtScores)) %>%
  head()

botext$region<- countrycode(botext$region, "iso2c", "country.name")

  
knitr::kables(list(
  kable(caption = "Most Extroverted", botext) %>% kable_styling(),
  kable(caption = "Least Extroverted", topext) %>% kable_styling()
  )
) %>% kable_styling()

```


When looking at extrovertism, countries that are more 'globalized', e.g. North America and East Asia are more extroverted, compared to Africa and South America. When looking at the most and least extroverted, it seems like there's a smattering of locations from various corners of the world. 

When looking at the list of least extroverted countries, they're not 'well-known' countries on a global scale. Due to this, it's possible they've become more introverted as they don't regularly encounter new people/foreigners on a day-to-day basis.^'[Did you know that tourists have to pay 200 dollars per day to stay in Bhutan, which consistently ranks as one of the happiest countries? https://www.oneworldeducation.org/our-students-writing/bhutan-the-worlds-happiest-country/]


```{r, est world map, layout="l-body-outset", fig.cap="Diamond sadasds"}

esttablec <- esttable %>% 
  cbind(data$country)

colnames(esttablec)[13] <- "region"

esttablec <- esttablec %>%
  group_by(region) %>%
  drop_na 

for (i in redcount) {
  esttablec<- subset(esttablec, region!=i)
}

estworld <- esttablec %>% 
  group_by(region) %>%
  summarize(estScores = mean(estscore))


mergemapest <- inner_join(world_map, estworld, by = "region")


pest <- ggplot() +
  geom_polygon(data=mergemapest,
          aes(x=Longitude, y=Latitude, group=group, fill = estScores, label=region),
          color="white", size = 0.2) + 
  coord_cartesian(ylim = c(-50, 90)) + 
  labs(
    title="Neuroticism Scores of the World",
    subtitle="Africa is feeling colorful!",
    fill="Neuroticism  
Averages", 
  )+ theme_minimal() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.x = element_blank(),axis.title.y = element_blank())

ggplotly(pest)
```

Higher scores are correlated with being calm, lower scores are correlated being limbic.  


```{r, estworldtable}

topest <- estworld %>%
  arrange(estScores) %>%
  head()

topest$region<- countrycode(topest$region, "iso2c", "country.name")

botest <- estworld %>%
  arrange(desc(estScores)) %>%
  head()

botest$region<- countrycode(botest$region, "iso2c", "country.name")

  

knitr::kables(list(
  kable(caption = "Most Calm", botest) %>% kable_styling(),
  kable(caption = "Least Calm", topest) %>% kable_styling()
  )
) %>% kable_styling()

##RENAME LEGEND TITLES

```

It seems like the south-eastern part of the world is less limbic, specifically Africa and East Asia. I find it funny that China specifically is seen to be relatively 'calm', as they are notorious for bad work-life balances^[e.g. the 996 schedule of working from 9am to 9pm, 6 days a week], the 'lie down' movement^[Youth in China are adopting the philosophy of 'lying down' and giving up, due to the bad job market after graduation. They often feel let down by their society, as they've always been taught that studying hard and getting into a good university will lead to a good life. Yet, when they graduate, they struggle to find jobs and keep themselves afloat.] -- things that show the 'mentally-difficult' conditions that they are living it. 

Yet, it's also reasonable to say that Chinese people are accustomed to high stress when dealing with academic pressures.^[E.g. To get into university, students take the Gaokao, a two-day standardized test that determines their entire future.] Hence, they might have learned to become more emotionally stable. 


```{r, csn world map, layout="l-body-outset", fig.cap="Diamonddassda sadasds"}

csntablec <- csntable %>% 
  cbind(data$country)

colnames(csntablec)[13] <- "region"

csntablec <- csntablec %>%
  group_by(region) %>%
  drop_na 

for (i in redcount) {
  csntablec<- subset(csntablec, region!=i)
}

csnworld <- csntablec %>% 
  group_by(region) %>%
  summarize(csnScores = mean(csnscore))


mergemapcsn <- inner_join(world_map, csnworld, by = "region")


pcsn <- ggplot() +
  geom_polygon(data=mergemapcsn,
          aes(x=Longitude, y=Latitude, group=group, fill = csnScores, label=region),
          color="white", size = 0.2) + 
  coord_cartesian(ylim = c(-50, 90)) + 
  labs(
    title="Conscientiousness Scores of the World",
    subtitle="Africa is feeling colorful!",
    fill="conscientiousness 
Averages", 
  )+ theme_minimal() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.x = element_blank(),axis.title.y = element_blank())

ggplotly(pcsn)


```

Higher scores are correlated with organization and contentiousness, lower scores are correlated carelessness.  

```{r, csnworldtable}

topcsn <- csnworld %>%
  arrange(csnScores) %>%
  head()

topcsn$region<- countrycode(topcsn$region, "iso2c", "country.name")

botcsn <- csnworld %>%
  arrange(desc(csnScores)) %>%
  head()

botcsn$region<- countrycode(botcsn$region, "iso2c", "country.name")

  

knitr::kables(list(
  kable(caption = "Most Contentious", botcsn) %>% kable_styling(),
  kable(caption = "Least Contentious", topcsn) %>% kable_styling()
  )
) %>% kable_styling()

```

For conscientiousness, Africa is lit up like a Christmas tree! North America is also pretty light. On the other hand, South America is quite dark. 

I also find it interesting that Asia, which is known for their ability to work hard and focus, seem to be quite average. Perhaps, this is where capitalism excels. 

Conscientious people are typically correlated with success, as they're able to complete their work thoroughly. With this hard work, they're able to suceed more in capitalistic countries.


cheerio!!! \@ref(fig:opn world map) wahahaa


```{r, agr world map, layout="l-body-outset", fig.cap="Diamond sadasds"}

agrtablec <- agrtable %>% 
  cbind(data$country)

colnames(agrtablec)[13] <- "region"

agrtablec <- agrtablec %>%
  group_by(region) %>%
  drop_na 

for (i in redcount) {
  agrtablec<- subset(agrtablec, region!=i)
}

agrworld <- agrtablec %>% 
  group_by(region) %>%
  summarize(agrScores = mean(agrscore))

mergemapagr <- inner_join(world_map, agrworld, by = "region")


pagr <- ggplot() +
  geom_polygon(data=mergemapagr,
          aes(x=Longitude, y=Latitude, group=group, fill = agrScores, label=region),
          color="white", size = 0.2) + 
  coord_cartesian(ylim = c(-50, 90)) + 
  labs(
    title="Agreeableness Scores of the World",
    subtitle="Africa is feeling colorful!",
    fill="Agreeableness
Averages", 
  )+ theme_minimal() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.x = element_blank(),axis.title.y = element_blank())

ggplotly(pagr)

##Only one td,ne score, km, pw, tj, GQ

```

Higher scores are correlated with agreeableness, lower scores are correlated egocentrism.  



```{r, agrworldtable}

topagr <- agrworld %>%
  arrange(agrScores) %>%
  head()

topagr$region<- countrycode(topagr$region, "iso2c", "country.name")

botagr <- agrworld %>%
  arrange(desc(agrScores)) %>%
  head()

botagr$region<- countrycode(botagr$region, "iso2c", "country.name")
  

knitr::kables(list(
  kable(caption = "Most Agreeable", botagr) %>% kable_styling(),
  kable(caption = "Least Agreeable", topagr) %>% kable_styling()
  )
) %>% kable_styling()

```

Agreeableness looks pretty similar to the contenciousness graph. It's difficult to not find the most agreeable countries the most egotistical, as they must think they're always so agreeable! However, you can just say that these countries value politeness highly. 

It's also interesting to note that Asian countries typically are very resepctful of their elders, and bend to their will. This idea is not really represented within this graph. 


```{r opn world map, layout="l-body-outset", fig.cap="Diamond Prices"}

opntablec <- opntable %>% 
  cbind(data$country)

colnames(opntablec)[13] <- "region"

opntablec <- opntablec %>%
  group_by(region) %>%
  drop_na 

for (i in redcount) {
  opntablec<- subset(opntablec, region!=i)
}

opnworld <- opntablec %>% 
  group_by(region) %>%
  summarize(opnScores = mean(opnscore))

mergemapopn <- inner_join(world_map, opnworld, by = "region")


popn <- ggplot() +
  geom_polygon(data=mergemapopn,
          aes(x=Longitude, y=Latitude, group=group, fill = opnScores, label=region),
          color="white", size = 0.2) + 
  coord_cartesian(ylim = c(-50, 90)) + 
  labs(
    title="Openness Scores of the World",
    fill="Openness
Averages", 
  )+ theme_minimal() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.title.x = element_blank(),axis.title.y = element_blank())

ggplotly(popn)


# https://rstudio.github.io/distill/figures.html for making figures expand 
#figure out better words for inquistiion/not oppeness
```

Higher scores are correlated with inquisition, lower scores are correlated indifference. 



```{r, opnworldtable}

topopn <- opnworld %>%
  arrange(opnScores) %>%
  head()

topopn$region<- countrycode(topopn$region, "iso2c", "country.name")

botopn <- opnworld %>%
  arrange(desc(opnScores)) %>%
  head()

botopn$region<- countrycode(botopn$region, "iso2c", "country.name")

  

knitr::kables(list(
  kable(caption = "Most Inquisitive", botopn) %>% kable_styling(),
  kable(caption = "Least Inquisitve", topopn) %>% kable_styling()
  )
) %>% kable_styling()

```

The southern hemisphere seems to be more open compared to the Northern hemisphere, with Europe being the exception. 

### Are All Questions Created Equal? <a name="questions"></a>

We can also analyze the questions themselves. A funky little thing that this quiz did, was record how many milliseconds each respondent spent on each question. That seems like a fun thing to look at....

Thus, I present to you: General time spent on each question!

```{r, rtimext}
rtimeext <- data %>%
  select(c (ends_with('_E'))) %>% 
  select(c(starts_with('EXT'))) %>%
  sapply("/", 1000)

rtimeext=as.data.frame(rtimeext)

rtimeext <- rtimeext %>%
  filter(EXT1_E < 20) %>%
  filter(EXT2_E < 20) %>%
  filter(EXT3_E < 20) %>%
  filter(EXT4_E < 20) %>%
  filter(EXT5_E < 20) %>%
  filter(EXT6_E < 20) %>%
  filter(EXT7_E < 20) %>%
  filter(EXT7_E > 0) %>%
  filter(EXT8_E < 20) %>%
  filter(EXT9_E < 20) %>%
  filter(EXT10_E < 20) %>%
  slice_sample(n=500) 


rqextp<-rtimeext  %>%  
  pivot_longer(everything(), values_to="Seconds", names_to="Question") %>% 
  ggplot() +
  geom_boxplot(aes(x=Question, y=Seconds))

```

```{r}
###
rtimeCSN <- data %>%
  select(c (ends_with('_E'))) %>% 
  select(c(starts_with('CSN'))) %>%
  sapply("/", 1000)

rtimeCSN=as.data.frame(rtimeCSN)

rtimeCSN <- rtimeCSN %>%
  filter(CSN1_E < 20) %>%
  filter(CSN2_E < 20) %>%
  filter(CSN3_E < 20) %>%
  filter(CSN4_E < 20) %>%
  filter(CSN5_E < 20) %>%
  filter(CSN6_E < 20) %>%
  filter(CSN7_E < 20) %>%
  filter(CSN7_E > 0) %>%
  filter(CSN8_E < 20) %>%
  filter(CSN9_E < 20) %>%
  filter(CSN10_E < 20) %>%
  slice_sample(n=500) 


rqcsnp <- rtimeCSN  %>%  
  pivot_longer(everything(), values_to="Seconds", names_to="Question") %>% 
  ggplot() +
  geom_boxplot(aes(x=Question, y=Seconds))

###
rtimeEST <- data %>%
  select(c (ends_with('_E'))) %>% 
  select(c(starts_with('EST'))) %>%
  sapply("/", 1000)

rtimeEST=as.data.frame(rtimeEST)

rtimeEST <- rtimeEST %>%
  filter(EST1_E < 20) %>%
  filter(EST2_E < 20) %>%
  filter(EST3_E < 20) %>%
  filter(EST4_E < 20) %>%
  filter(EST5_E < 20) %>%
  filter(EST6_E < 20) %>%
  filter(EST7_E < 20) %>%
  filter(EST7_E > 0) %>%
  filter(EST8_E < 20) %>%
  filter(EST9_E < 20) %>%
  filter(EST10_E < 20) %>%
  slice_sample(n=500) 


rqestp <- rtimeEST  %>%  
  pivot_longer(everything(), values_to="Seconds", names_to="Question") %>% 
  ggplot() +
  geom_boxplot(aes(x=Question, y=Seconds))

###
rtimeAGR <- data %>%
  select(c (ends_with('_E'))) %>% 
  select(c(starts_with('AGR'))) %>%
  sapply("/", 1000)

rtimeAGR=as.data.frame(rtimeAGR)

rtimeAGR <- rtimeAGR %>%
  filter(AGR1_E < 20) %>%
  filter(AGR2_E < 20) %>%
  filter(AGR3_E < 20) %>%
  filter(AGR4_E < 20) %>%
  filter(AGR5_E < 20) %>%
  filter(AGR6_E < 20) %>%
  filter(AGR7_E < 20) %>%
  filter(AGR7_E > 0) %>%
  filter(AGR8_E < 20) %>%
  filter(AGR9_E < 20) %>%
  filter(AGR10_E < 20) %>%
  slice_sample(n=500) 


rqagrp<- rtimeAGR  %>%  
  pivot_longer(everything(), values_to="Seconds", names_to="Question") %>% 
  ggplot() +
  geom_boxplot(aes(x=Question, y=Seconds))

###
rtimeOPN <- data %>%
  select(c (ends_with('_E'))) %>% 
  select(c(starts_with('OPN'))) %>%
  sapply("/", 1000)

rtimeOPN=as.data.frame(rtimeOPN)

rtimeOPN <- rtimeOPN %>%
  filter(OPN1_E < 20) %>%
  filter(OPN2_E < 20) %>%
  filter(OPN3_E < 20) %>%
  filter(OPN4_E < 20) %>%
  filter(OPN5_E < 20) %>%
  filter(OPN6_E < 20) %>%
  filter(OPN7_E < 20) %>%
  filter(OPN7_E > -1) %>%
  filter(OPN8_E < 20) %>%
  filter(OPN9_E < 20) %>%
  filter(OPN10_E < 20) %>%
  slice_sample(n=500) 


rqopnp <- rtimeOPN  %>%  
  pivot_longer(everything(), values_to="Seconds", names_to="Question") %>% 
  ggplot() +
  geom_boxplot(aes(x=Question, y=Seconds))


rqextp
rqcsnp
rqestp
rqagrp
rqopnp

```


This is a good visual to compare questions to each other, especially questions in the same category. 

For your reference: 

- EXT = Extroversion (S/R)
- EST = Neuroticsm (L/C)
- CSN = Organization (O/U)
- AGR = Agreeableness (A/E)
- OPN = Openness (I/U)

For those unaware, this is a box plot^[I actually forgot this type of graph existed, until I was randomly scrolling through the ggplot2 library of different graph types!]. The white box symbolizes the interquartile range, with the lower half of the box showing the bottom 25%, while the top half of the box shows the top 25%. The line in the center is the median of the question. It's really good for visualizing the spread of data (which seems to range quite a bit). However, I've skewed the data by cutting off any values above 20 seconds^[as it's quite uncommon and makes plotting the graph difficult] and only took a random sample of 500 response times for each question^[500 is enough to show the general trend, and utilizing more only makes graphs take longer to load.]. 

However, I want to be more precise with these loading times, so I've specifically pulled the questions that take the longest and shortest times to complete. 


```{r, questiontimes}
qtime <- data %>%
  select(c (ends_with('_E')))

qtimeframe <- data.frame(qtime)  %>%
  slice_sample(n=100) %>%
  colMeans() 

qtimes <- data.table::as.data.table(qtimeframe, .keep.rownames = "word")
qcolnames <- colnames(qtime) 


qtimes <- mutate(qtimes, question = qcolnames) %>%
  select(question, everything())%>%
  arrange(desc(qtimeframe)) 



highqtime <- qtimes %>%
  slice(2:6) %>% 
  mutate(qtimeframe =  qtimeframe/1000) %>%
  mutate(qs = c("I shirk my duties.", "I leave my belongings around.", "I am relaxed most of the time.", "I feel little concern for others.", "I don't like to draw attention to myself.")) %>%
  relocate(question, qs, qtimeframe)


lowqtime <- qtimes %>%
  slice (46:50) %>% 
  mutate(qtimeframe =  qtimeframe/1000) %>%
  mutate(qs = c("I use difficult words.", "I often feel blue.", "I have excellent ideas.", "I am full of ideas.", "I have a rich vocabulary."))%>%
  relocate(question, qs, qtimeframe)

colnames(highqtime) <- c("Category", "Question", "Time in Seconds")
colnames(lowqtime) <- c("Category", "Question", "Time in Seconds")

knitr::kables(list(
  kable(caption = "Questions That Took the Longest", highqtime) %>% kable_styling(),
  kable(caption = "Questions That Took the Shortest", lowqtime) %>% kable_styling()
  )
) %>% kable_styling()
```


I've taken the liberty of removing EXT_1 (the first question on the quiz), which had an average score of 87 seconds. This is likely because people people were getting accustomed to the quiz, had loading time issues, or started the quiz, then immediately forgot about it. 

"I shirk my duties" took the longest, likely because 'shirk' is an uncommon word and people wanted to search up the definition, which easily could've taken an extra 10 seconds. As for the other questions, they're all relatively long sentences and have more nuance. They're all very situational, as people are rarely "always relaxed" or "never relaxed", and it takes time to think whether you're relax a MAJOURITY of the time. Same thing for little concern for others - there are tons of people you care about, but also, tons of people you don't. So, it's a bit tricky to answer those. 

On the other hand, the questions that took the least amount of time are short and straightforward, and are obvious to judge yourself on. You either read a dictionary for fun to seem smart, or you don't. I do find it interesting that it's difficult for people to determine whether they're 'relaxed' rather than 'blue'. Likely because you conciously pay attention to when you're sad, but not when you're relaxed? You can also see that these questions are the ones that are asked later (e.g. AGR_9 is part of the 9th out of 10 rounds of questions, meaning that it'll be really close to the ending of the quiz). Anticipation for results may have caused them to rush through the later questions. 


Another interesting thing to note is the distrubtion of answers for each question. You may expected that each question has a distribution similar to standard deviation. However... that's actually not the case! Many questions tend to have a distribution like so: 

```{r}

## analyze the distrbution of responses for each of the high / low quetinos, maybe add into a grid? 

agr1p <- data %>%
  select('AGR1') %>%
  pivot_longer(everything(), values_to="Answers", names_to="Question") %>%
  filter(Answers != "0")

agr1g<- ggplot(data=agr1p, aes(x=Answers)) +
   geom_bar(fill="steel blue") +
   labs(
     title = "I shirk my duties.",
     subtitle = "I think we've solved procrasination") + 
   xlab("Respondent's Possible Answers") +
   ylab("Amount of Responses")+
   theme_minimal()

###
est3p <- data %>%
  select('AGR3') %>%
  pivot_longer(everything(), values_to="Answers", names_to="Question") %>%
  filter(Answers != "0")

est3g <- ggplot(data=est3p, aes(x=Answers)) +
   geom_bar(fill="steel blue") +
   labs(
     title = "I insult people.",
     subtitle = "Wholesome :)") + 
   xlab("Respondent's Possible Answers") +
   ylab("Amount of Responses")+
   theme_minimal()

###

agr8p <- data %>%
  select('AGR8') %>%
  pivot_longer(everything(), values_to="Answers", names_to="Question") %>%
  filter(Answers != "0")


agr8g <- ggplot(data=agr8p, aes(x=Answers)) +
   geom_bar(fill="steel blue") +
   labs(
     title = "I am relaxed most of the time.",
     subtitle = "Stress balls work..?") + 
   xlab("Respondent's Possible Answers") +
   ylab("Amount of Responses")+
   theme_minimal()

###

csn4p <- data %>%
  select('CSN4') %>%
  pivot_longer(everything(), values_to="Answers", names_to="Question") %>%
  filter(Answers != "0")


csn4g<- ggplot(data=csn4p, aes(x=Answers)) +
   geom_bar(fill="steel blue") +
   labs(
     title = "I feel little concern for others.	",
     subtitle = "Can't believe that the Internet is nice") + 
   xlab("Respondent's Possible Answers") +
   ylab("Amount of Responses")+
   theme_minimal()


csn8p <- data %>%
  select('CSN8') %>%
  pivot_longer(everything(), values_to="Answers", names_to="Question") %>%
  filter(Answers != "0")

csn8g <- ggplot(data=csn8p, aes(x=Answers)) +
   geom_bar(fill="steel blue") +
   labs(
     title = "I don’t like to draw 
attention to myself.",
     subtitle = "...") + 
   xlab("Respondent's Possible Answers") +
   ylab("Amount of Responses")+
   theme_minimal()

est9p <- data %>%
  select('EST9') %>%
  pivot_longer(everything(), values_to="Answers", names_to="Question") %>%
  filter(Answers != "0")


est9g <- ggplot(data=est9p, aes(x=Answers)) +
   geom_bar(fill="steel blue") +
   labs(
     title = "I have excellent ideas.",
     subtitle = "THINK GOOD! 10B STARTUP IDEA!") + 
   xlab("Respondent's Possible Answers") +
   ylab("Amount of Responses")+
   theme_minimal()


#grid.arrange(agr1g, est3g, agr8g, csn4g, csn8g, ncol=2)
plot_grid(agr1g, est3g, agr8g, csn4g, ncol = 2, align = "hv")
plot_grid(csn8g, est9g, ncol = 2, align = "hv")


```

There are four major types of distribution seen in the data: 

1. Logarithmic (First Row)

The columns progressively increase or decrease. I think these graphs are the most "trustworthy", as you'd only put 1 or 5 (the extremes) if you were incredibly confident in your answer.^[If you ask people to choose a number between 1 and 5, they tend to pick 2, 3, or 4, rather than 1 or 5.] Not only that, but these questions aren't really 'shameful' to admit, like "I get stressed out easily", which allows people to be honest and pick extremes. Questions also tend to be less 'situation' and more 'specific', where you can very clearly visualize what you'd be doing in that situation, rather than responding "Oh... sometimes I am, sometimes I'm not!" (E.g. "I am quiet" likely wouldn't follow this trend, but "I am quiet around strangers" probably does, because it helps narrow down the situation. You also don't really change your behavior around different strangers, you usually are pretty constant with your behavior.)

Some other examples include: 

- I have difficulty understanding abstract ideas.
- I am quiet around strangers.
- I have a soft heart.
- I spend time reflecting on things.

If you're wondering which side they skew on.... just trust your gut on it :)

2. Skewed (Second Row)

i feel like these are best associated with questions where self-bias is most prevalent, as you want to make yourself as something you're not (to make yourself feel better). These questions are also very situational; Sometimes I do this, sometimes I do. That's why people tend to move towards the middle. This is the most common distribution type. 


Examples include: 

- I make a mess of things.
- I get stressed out easily.  
- I leave my belongings around. 
- I follow a schedule. 

3. "Normal" Distribution (Third Row, Left)

I'm lying to you - This graph isn't normal distribution. I'm just calling it normal distribution because the answer 3 (neutral) is the most common answer. Quite frankly, it just means that people are either confused, or they don't really have a large opinion on it, so they're almost forced to choose 3. These questions seem to be the most 'observable/objective' of the bunch. Personally, I try to make a habit on avoiding clicking 3 no matter what (I'm not sure if others are the same), but it's still interesting to see. I feel like these things are not things to be 'proud' of or dislike about yourself, nor would you mention it unless prompted, which is likely why it's associated with the extrovertism questions. 

Examples Include: 

- I don't talk a lot.
- I keep in the background.

4. Relatively Random (Third Row, Right) 

So these are the ones that don't follow a trend. Well, what happens is that 1 and 5 are similar in height and have about 150k responses, while  3, 4, 5 are also similar in height, with about 250k responses. It's the kinds of questions that go "Yea... I'm definitely not SUPER ___, but it happens from time to time... I'm not sure how I would compare with other people though... so 2, 3, or 4 sound about right."

Examples Include: 

- I talk to a lot of different people at parties.
- I am easily disturbed.
- I often forget to put things back in their proper place.^[This one is almost inverted, where 2 and 4 are the most common responses, followed by 1 and 5, then 3.]
- I change my mood a lot.




<!--

rmarkdown::render('C:/Users/sophi/OneDrive/Documents/Personal/bigfive/docs/data.Rmd', output_file = 'C:/Users/sophi/OneDrive/Documents/Personal/bigfive/docs/data.html')

-->